SubsidyExplorer - Step 9: New Chair's text - management assumptions

### 2021-10-21 scripts/08_subs_affected.Rmd
mgmt implications of chair's text

This script outputs the amounts of subsidies affected by each discipline type (and/or definition) in SubsidyExplorer. This was requested by Anthony to aid in his analyses.

@@

write_csv(subs_affected_iuu_out, paste0(results_dir, "subs_affected_iuu_out.csv"))
```

@@

>>>>

This script outputs the amounts of subsidies affected by each discipline type (and/or definition) in SubsidyExplorer. This was requested by Anthony Rogers to aid in his analyses for Pew.

@@

write_csv(subs_affected_iuu_out, paste0(results_dir, "subs_affected_iuu_out.csv"))

# Now do the same by country
subs_affected_flag_iuu <- vessel_dat %>%
  group_by(iuu1, flag_iso3) %>%
  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "IUU - RFMO Lists") %>%
  relocate(description) %>%
  rename(affected = iuu1) %>%
  arrange(flag_iso3)

subs_affected_flag_disputed <- vessel_dat %>%
  group_by(is_disputed, flag_iso3) %>%
  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "IUU - Disputed Area") %>%
  relocate(description) %>%
  rename(affected = is_disputed) %>%
  arrange(flag_iso3)

subs_affected_flag_iuu_out <- subs_affected_flag_iuu %>%
  bind_rows(subs_affected_flag_disputed)

write_csv(subs_affected_flag_iuu_out, paste0(results_dir, "subs_affected_flag_iuu_out.csv"))
```

@@

```{r}
subs_affected_flag_oa1_median <- vessel_dat %>%
  group_by(oa1_median, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 1 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa1_median) %>%
  arrange(flag_iso3)

subs_affected_flag_oa1_w_mean <- vessel_dat %>%
  group_by(oa1_w_mean, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa1_w_mean) %>%
  arrange(flag_iso3)

subs_affected_flag_oa2_median <- vessel_dat %>%
  group_by(oa2_median, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 0.8 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa2_median) %>%
  arrange(flag_iso3)

subs_affected_flag_oa2_w_mean <- vessel_dat %>%
  group_by(oa2_w_mean, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa2_w_mean) %>%
  arrange(flag_iso3)

subs_affected_flag_oa3_median <- vessel_dat %>%
  group_by(oa3_median, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa3_median) %>%
  arrange(flag_iso3)

subs_affected_flag_oa3_w_mean <- vessel_dat %>%
  group_by(oa3_w_mean, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa3_w_mean) %>%
  arrange(flag_iso3)

subs_affected_flag_oa4_median <- vessel_dat %>%
  group_by(oa4_median, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa4_median) %>%
  arrange(flag_iso3)

subs_affected_flag_oa4_w_mean <- vessel_dat %>%
  group_by(oa4_w_mean, flag_iso3) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa4_w_mean) %>%
  arrange(flag_iso3)

subs_affected_flag_oa_out <- subs_affected_flag_oa1_median %>%
  bind_rows(subs_affected_flag_oa1_w_mean) %>%
  bind_rows(subs_affected_flag_oa2_median) %>%
  bind_rows(subs_affected_flag_oa2_w_mean) %>%
  bind_rows(subs_affected_flag_oa3_median) %>%
  bind_rows(subs_affected_flag_oa3_w_mean) %>%
  bind_rows(subs_affected_flag_oa4_median) %>%
  bind_rows(subs_affected_flag_oa4_w_mean)

write_csv(subs_affected_flag_oa_out, paste0(results_dir, "subs_affected_flag_overfished_out.csv"))
```

### 2021-10-21 scripts/09_chairs_text_mgmt.Rmd
mgmt implications of chair's text

title: "SubsidyExplorer - Step 7: Pre-Populated Proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

@@

end_year <- 2080

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)

@@

```{r}
proposal_results <- NULL

@@

    # Make list
    fleet_list <- fleet$summary %>%
      group_by(region) %>%
      group_split()
    names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)]

@@

    # Add to data frame
      proposal_results <- proposal_results %>%
        bind_rows(results_all)

@@

```{r}
all_results_global_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot)

@@

# Get rounded end values
global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff)

@@

```{r}
all_results_global_absolute_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
                                     TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                              Variable == "catches_total" ~ "Catches")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                abs_Diff_tot,
                Variable) %>%
  spread(Variable, abs_Diff_tot)

write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))

all_results_regional_absolute_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches")) %>%
  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
                              TRUE ~ 0)) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                abs_Diff,
                Variable) %>%
  spread(Variable, abs_Diff)

write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
```

```{r}
# Weight of a mature dairy cow in mt
cow_weight <- 0.6803886

all_results_global_cow_equivalent_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
                                     TRUE ~ 0),
            cow_Diff = abs_Diff_tot*cow_weight) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                              Variable == "catches_total" ~ "Catches")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                cow_Diff,
                Variable) %>%
  spread(Variable, cow_Diff)

write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))

all_results_regional_cow_equivalent_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches")) %>%
  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
                              TRUE ~ 0),
         cow_Diff = abs_Diff*cow_weight) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                cow_Diff,
                Variable) %>%
  spread(Variable, cow_Diff)

write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))

@@

>>>>

title: "SubsidyExplorer - Step 9: New Chair's text - management assumptions"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

This script explores a couple of different assumptions regarding the exception in the newest Chair's text

@@

# End year for projections
end_year <- 2080

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "09-chairs-text-mgmt/"), "mgmt_threshold_", managed_cutoff, "/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
proposal_settings <- read.csv(here::here("data", "lookup-tables", "chairs_text_proposal_settings.csv"), stringsAsFactors = F)

@@

```{r}
proposal_results <- NULL
affected_subs <- NULL

@@

    # # Summarize fleet breakdown by country and save
    fleet_summary_country <- fleet$vessels %>%
      group_by(flag_iso3, development_status) %>%
      summarize(all_subs = sum(bad_ugly_subs, na.rm = T), removed_subs = sum(removed_subs, na.rm = T)) %>%
      ungroup() %>%
      mutate(percent_removed = round(case_when(all_subs == 0 ~ 0,
                                      TRUE ~ (removed_subs/all_subs)*100), 2)) %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name),
             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))

    # Make fleet list for model
    fleet_list <- fleet$summary %>%
      group_by(region) %>%
      group_split()
    names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)]

@@

    # Add to data frames
      proposal_results <- proposal_results %>%
        bind_rows(results_all)

      affected_subs <- affected_subs %>%
        bind_rows(fleet_summary_country)

@@

```{r}
all_results_global_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot) %>%
  arrange(Year)

@@

# # Get rounded end values
# global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# 
# global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff) %>%
  arrange(Year, Region)

@@

```{r}
# all_results_global_absolute_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#   summarize(BAU_tot = sum(BAU, na.rm = T),
#             Reform_tot = sum(Reform, na.rm = T),
#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
#                                      TRUE ~ 0)) %>%
#   ungroup() %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                               Variable == "catches_total" ~ "Catches")) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 abs_Diff_tot,
#                 Variable) %>%
#   spread(Variable, abs_Diff_tot)
# 
# write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
# 
# all_results_regional_absolute_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                                 Variable == "catches_total" ~ "Catches")) %>%
#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
#                               TRUE ~ 0)) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 Region,
#                 abs_Diff,
#                 Variable) %>%
#   spread(Variable, abs_Diff)
# 
# write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
```

```{r}
# Weight of a mature dairy cow in mt
# cow_weight <- 0.6803886
# 
# all_results_global_cow_equivalent_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#   summarize(BAU_tot = sum(BAU, na.rm = T),
#             Reform_tot = sum(Reform, na.rm = T),
#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
#                                      TRUE ~ 0),
#             cow_Diff = abs_Diff_tot*cow_weight) %>%
#   ungroup() %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                               Variable == "catches_total" ~ "Catches")) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 cow_Diff,
#                 Variable) %>%
#   spread(Variable, cow_Diff)
# 
# write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
# 
# all_results_regional_cow_equivalent_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                                 Variable == "catches_total" ~ "Catches")) %>%
#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
#                               TRUE ~ 0),
#          cow_Diff = abs_Diff*cow_weight) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 Region,
#                 cow_Diff,
#                 Variable) %>%
#   spread(Variable, cow_Diff)
# 
# write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))

@@

## Save Percent Affected Subs by Country

```{r}
affected_subs <- affected_subs %>%
  arrange(flag_iso3, run_id) %>%
  dplyr::select(-all_subs, -removed_subs)

write.csv(affected_subs, paste0(results_dir, "percent_subs_removed_by_country.csv"))
```
